### 2023-07-27 python_excel_ite.tex
draft ready for detailed final proofreading

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Spreadsheet modeling with Python}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Spreadsheet modeling with Python}

@@

At our institution, The EwP module is part of a business course entitled  \href{http://www.sba.oakland.edu/faculty/isken/courses/mis6900}{Advanced Analytics with Python} (AAP). The students taking this course have already taken the PCDA course within which they learned fundamental Python programming within the context of data analytics over seven weeks. The PCDA course ends with intro to the \href{https://scikit-learn.org/stable/index.html}{scikit-learn library} for doing predictive modeling in Python and the AAP course begins where the PCDA course ends. The EwP module could also be used as part of a semester long Python based analytics course. Most AAP students have also already taken   \href{http://www.sba.oakland.edu/faculty/isken/courses/mis5460}{Business Analytics} (BA) which is a spreadsheet based introduction to business analytics. We do not strictly require the spreadsheet based course be taken before the PCDA or AAP courses as that course draws students from outside of our business programs who are strictly interested in programmatic tools such as Python. The BA and PCDA courses have historically been offered in face to face mode in a computer teaching lab. Since 2020, these two courses have been also offered as online, asynchronous courses. The newer AAP course has been offered since 2021 in an online asynchronous mode. All three courses have \href{http://www.sba.oakland.edu/Faculty/isken/teaching.html}{extensive course websites} that are publicly accessible, including access to all of the video content and supporting files.

@@

\subsection{Notebook 1: Modeling and data tables}

The stage is set with an overview of a typical spreadsheet based model that most of the students have seen before -- see Figure \ref{fig:stage}. The notebook also includes a screenshot (Figure \ref{fig:xl_model}) of a typical Excel model.

@@

\begin{figure}[!ht]
	\centering
	\begin{minipage}{.80\textwidth}
		\includegraphics[width=1.0\textwidth]{images/output_2_0.png}
	\end{minipage}
	\caption{Typical spreadsheet model}
	\label{fig:xl_model}
\end{figure}

@@

\begin{figure*}[!htbp]
	\centering
	\caption{Instantiating model inputs}
	\includegraphics[scale=0.5]{images/model_inputs.png}
	\label{fig:model_inputs}
\end{figure*}

@@

\begin{figure*}[!htbp]
	\centering
	\caption{A 2-way data table}
	\includegraphics[scale=0.5]{images/function_datatable.png}
	\label{fig:function_datatable}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\caption{Scatter plot based on 2-way data table}
	\includegraphics[scale=0.5]{images/datatable_scatter.png}
	\label{fig:datatable_scatter}
\end{figure*}

@@

\begin{figure}[!ht]
	\centering
	\begin{minipage}{.80\textwidth}
		\includegraphics[width=1.0\textwidth]{images/two_way_dt.png}
	\end{minipage}
	\caption{Faceted plot based on 2-way data table}
	\label{fig:2way_dt}
\end{figure}

\subsection{Notebook 2: Goal seek}

@@

\subsection{Notebook 3: Monte-Carlo simulation}

@@

\begin{figure*}[!htbp]
	\centering
	\caption{Design specification for \code{simulate()} function}
	\includegraphics[scale=0.5]{images/oo_sim_design_specs.png}
	\label{fig:oo_sim_design_specs}
\end{figure*}

@@

\begin{figure}[!ht]
	\centering
	\begin{minipage}{.80\textwidth}
		\includegraphics[width=1.0\textwidth]{images/boxplots.png}
	\end{minipage}
	\caption{Profit boxplots by order quantity}
	\label{fig:boxplot}
\end{figure}

@@

\begin{figure*}[!htbp]
	\centering
	\caption{Closing thoughts in simulation notebook}
	\includegraphics[scale=0.5]{images/sim_wrapup.png}
	\label{fig:sim_wrapup}
\end{figure*}

@@

\subsection{Notebook 4: Project packaging}

@@

\subsection{Notebook 5: Documentation}

>>>>

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Spreadsheet-ish modeling with Python}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Spreadsheet-ish modeling with Python}

@@

At our institution, The EwP module is part of a business course entitled  \href{http://www.sba.oakland.edu/faculty/isken/courses/mis6900}{Advanced Analytics with Python} (AAP). The students taking this course have already taken the PCDA course within which they learned fundamental Python programming within the context of data analytics over seven weeks. The PCDA course ends with intro to the \href{https://scikit-learn.org/stable/index.html}{scikit-learn library} for doing predictive modeling in Python and the AAP course begins where the PCDA course ends. The EwP module could also be used as part of a semester long Python based analytics course. Most AAP students have also already taken   \href{http://www.sba.oakland.edu/faculty/isken/courses/mis5460}{Business Analytics} (BA) which is a spreadsheet based introduction to business analytics. We do not strictly require the spreadsheet based course be taken before the PCDA or AAP courses as that course draws students from outside of our business programs who are strictly interested in programmatic tools such as Python. The BA and PCDA courses have historically been offered in face to face mode in a computer teaching lab. Since 2020, these two courses have been also offered as online, asynchronous courses. The newer AAP course has been offered since 2021 in an online asynchronous mode. All three courses have extensive course websites that are publicly accessible, including access to all of the video content and supporting files.

@@

\subsection{Notebook 1: Modeling and data tables (\href{http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_1_model_datatable.html}{html version})}

The stage is set with an overview of a typical spreadsheet based model that most of the students have seen before.

@@

The notebook also includes a screenshot (Figure \ref{fig:xl_model}) of a typical Excel model.

\begin{figure}[!htbp]
	\includegraphics[width=1.0\textwidth]{images/output_2_0.png}
	\caption{Typical spreadsheet model}
	\label{fig:xl_model}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/model_inputs.png}
	\caption{Instantiating model inputs}
	\label{fig:model_inputs}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/function_datatable.png}
	\caption{A 2-way data table}
	\label{fig:function_datatable}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/datatable_scatter.png}
	\caption{Scatter plot based on 2-way data table}
	\label{fig:datatable_scatter}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1.0\textwidth]{images/two_way_dt.png}
	\caption{Faceted plot based on 2-way data table}
	\label{fig:2way_dt}
\end{figure}

\subsection{Notebook 2: Goal seek (\href{http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_2_goalseek.html}{html version})}

@@

\subsection{Notebook 3: Monte-Carlo simulation (\href{http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_3_simulation.html}{html version})}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/oo_sim_design_specs.png}
	\caption{Design specification for \code{simulate()} function}
	\label{fig:oo_sim_design_specs}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1.0\textwidth]{images/boxplots.png}
	\caption{Profit boxplots by order quantity}
	\label{fig:boxplot}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/sim_wrapup.png}
	\caption{Closing thoughts in simulation notebook}
	\label{fig:sim_wrapup}
\end{figure}

@@

\subsection{Notebook 4: Project packaging (\href{http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_4_project_packaging.html}{html version})}

@@

\subsection{Notebook 5: Documentation (\href{http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_5_documentation.html}{html version})}
